\normalfont\spacedallcaps{Programmentwurf}

### 2022-04-08 Chess-AdvancedSE/Docs/Doku/newDoku/article_4.tex
schönere doku in newDoku added

\documentclass{article}
\usepackage{graphicx}
\usepackage{hyperref}

% better color names
\usepackage[dvipsnames,table]{xcolor}

% listings
\usepackage{listings}

\lstdefinestyle{mStyle}{
    basicstyle=\linespread{1.0}\normalsize\ttfamily,
    keepspaces=false,
    keywordstyle=\color{Fuchsia},
    identifierstyle=\color{MidnightBlue},
    commentstyle=\color{Green},
    stringstyle=\color{Mahogany},
    columns=flexible
}

\title{Programmentwurf für Check-Mate}
\author{Moritz Knapp  \\
	SICK AG  \\
	\and 
	David Schmidt \\
	SICK AG \\
	}

\date{\today}
\begin{document}

\maketitle

\tableofcontents
\newpage

@@

>>>>

\documentclass[
10pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}

\input{structure.tex} % Include the structure.tex file which specified the document structure and layout
\hyphenation{Fortran hy-phen-ation} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

%----------------------------------------------------------------------------------------
%	TITLE AND AUTHOR(S)
%----------------------------------------------------------------------------------------

\title{\normalfont\spacedallcaps{Programmentwurf}} % The article title

\subtitle{Check-Mate} % Uncomment to display a subtitle

\author{\spacedlowsmallcaps{David Schmidt \& Moritz Knapp}} % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block

\date{} % An optional date to appear under the author(s)

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADERS
%----------------------------------------------------------------------------------------

\renewcommand{\sectionmark}[1]{\markright{\spacedlowsmallcaps{#1}}} % The header for all pages (oneside) or for even pages (twoside)
%\renewcommand{\subsectionmark}[1]{\markright{\thesubsection~#1}} % Uncomment when using the twoside option - this modifies the header on odd pages
\lehead{\mbox{\llap{\small\thepage\kern1em\color{halfgray} \vline}\color{halfgray}\hspace{0.5em}\rightmark\hfil}} % The header style

\pagestyle{scrheadings} % Enable the headers specified in this block

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS & LISTS OF FIGURES AND TABLES
%----------------------------------------------------------------------------------------

\maketitle % Print the title/author/date block

\setcounter{tocdepth}{2} % Set the depth of the table of contents to show sections and subsections only

\tableofcontents % Print the table of contents

\listoffigures % Print the list of figures

\newpage % Start the article content on the second page, remove this if you have a longer abstract that goes onto the second page

@@

%\renewcommand{\refname}{\spacedlowsmallcaps{References}} % For modifying the bibliography heading

%\bibliographystyle{unsrt}

%\bibliography{sample.bib} % The file containing the bibliography

%----------------------------------------------------------------------------------------
